---
output: rmarkdown::github_document
---

Interpolate a time series of polygons with areal weighting through tidyr::nest and purrr::map.

# Packages

```{r pac, warning = FALSE, message = FALSE}

library(tidyverse)
library(viridis)
library(sf)
library(reprex)

```

# Data

Package sf includes sample data described at https://r-spatial.github.io/spdep/articles/sids.html.

```{r dat, warning = FALSE, message = FALSE}

demo(nc, 
     ask = FALSE, 
     echo = FALSE)

```

\newpage

# Wrangle

Wrangle the North Carolina SIDS dataset to (a) a time series of intensive data and (b) a reference grid.

```{r wra, warning = FALSE, message = FALSE}

# (a)
dat = 
  nc %>% 
  mutate(PNWBIR74 = NWBIR74 / BIR74,
         PNWBIR79 = NWBIR79 / BIR79) %>% # Calculate intensive columns (%).
  select(PNWBIR74,
         PNWBIR79) %>% # Cut extensive columns.
  data.frame %>% # Switch geometries to non-sf column for pivot_longer.
  pivot_longer(cols = c(PNWBIR74,
                        PNWBIR79),
               names_to = "year",
               values_to = "perc") %>% # Pivot for consistency w/ use case.
  mutate(year = ifelse(year == "PNWBIR74",
                       1974,
                       1979)) %>% # Get years into numeric.
  data.frame %>% # Get class back to data.frame. This doesn't matter.
  st_sf %>% # Get geometries back to sf.
  rename(geometry = geom) # Fix geometries name for rbind w/ interpolation output.

# (b)
ref = 
  nc %>% 
  st_make_grid(n = c(20, 
                     10)) # Get a grid for interpolation.

```

\newpage

# Run

Interpolate the time series of intensive data onto the reference grid, with (b) and without (a) explicit time.

```{r run, warning = FALSE, message = FALSE}

# Get results w/o accounting for years.
out_wrong = 
  dat %>% 
  st_interpolate_aw(to = ref,
                    extensive = FALSE) %>% 
  mutate(year = "(Interpolated)") %>% 
  select(-Group.1) %>% 
  rbind(dat)

# Get results w/ explicit years. 
out_right = 
  dat %>% 
  group_by(year) %>% 
  nest %>% # Turn data into a list column by year.
  mutate(Output = 
           data %>% 
           map(.f = st_interpolate_aw,
               to = ref,
               extensive = FALSE) %>% # Interpolate data to the reference grid.
           map(.f = select,
               -Group.1), # Tag on explicit identifier for output.
         Input = 
           data %>% 
           map(.x = .,
               .f = data.frame)) %>% 
  select(-data) %>% 
  pivot_longer(cols = c("Input",
                        "Output"),
               names_to = "names",
               values_to = "data") %>% 
  unnest %>% # Get data back out of the list column.
  ungroup %>% 
  data.frame %>% 
  rbind %>% 
  st_sf

```

\newpage

# Visualize

Illustrate the input and output without explicit years. 

```{r vis_wrong}

ggplot() + 
  geom_sf(data = out_wrong, 
          aes(fill = perc), 
          color = NA) + 
  geom_sf(data = ref,
          fill = NA,
          color = "grey50",
          size = 0.25) +
  facet_wrap(~ year,
             ncol = 1) + 
  scale_fill_viridis() + 
  theme_void() +
  theme(legend.position = "none")

```

\newpage

Illustrate the input and output with explicit years.

```{r vis_right}

ggplot() + 
  geom_sf(data = out_right, 
          aes(fill = perc), 
          color = NA) + 
  geom_sf(data = ref,
          fill = NA,
          color = "grey50",
          size = 0.25) +
  facet_wrap(year ~ names) + 
  scale_fill_viridis() + 
  theme_void() +
  theme(legend.position = "none")

```

